Forecasting the 2024 U.S. Presidential Election: A Poll-Based Approach

### 2024-11-04 paper/paper.qmd
Applied use of parquet files for analysis data.

library(tidyverse)
library(skimr)
library(knitr)
library(GGally)
library(dplyr)
library(broom)
library(styler)
library(lubridate)
library(validate)
```

@@

```{r}
#| echo: false
#| message: false
#| warning: false
#| include: false
data <- read.csv("../data/02-analysis_data/cleaned_president_polls.csv")
```

@@

We would like to express our gratitude to the developers and contributors of the R programming language by @citeR and its ecosystem of packages, which have been invaluable in conducting this research. The **tidyverse** collection by @tidyverse, particularly its extensive functionality for data manipulation and visualization, has greatly enhanced the clarity and effectiveness of our analysis.

>>>>

library(tidyverse)
library(skimr)
library(knitr)
library(GGally)
library(dplyr)
library(broom)
library(styler)
library(lubridate)
library(validate)
library(arrow)
```

@@

```{r}
#| echo: false
#| message: false
#| warning: false
#| include: false
data <- read_parquet("../data/02-analysis_data/cleaned_president_polls.parquet")
```

@@

We would like to express our gratitude to the developers and contributors of the R programming language by @citeR and its ecosystem of packages, which have been invaluable in conducting this research. The **tidyverse** collection by @tidyverse, particularly its extensive functionality for data manipulation and visualization, has greatly enhanced the clarity and effectiveness of our analysis, and **arrow** package by @arrow enables us to work with parquet files.
